### 2019-03-19 5_evaluation.tex
Add table with version numbers.
Update graphs for evaluation.

\input{e1_metg_compute}

>>>>

\input{e0_flags}

We now present a comprehensive evaluation of Task Bench on up to 256
Haswell nodes of the Cori supercomputer~\cite{Cori}, a Cray XC40
machine. Cori Haswell nodes have 2 sockets with Intel Xeon E5-2698 v3
processors (total of 32 physical cores per node), 128 GB RAM, and a
Cray Aries interconnect. We use GCC 7.3.0 for compiling all Task Bench
implementations, and (where applicable) the system default MPI
implementation, Cray MPICH 7.7.3. Additional versions and flags for the
various systems are shown in Table~\ref{tab:flags}.

\subsection{Peak Performance and Efficiency}

\input{e1_flops}
\input{e2_efficiency}

\subsection{Overhead and Scalability}

\input{e3_metg_compute}

\subsection{Load Imbalance}

\subsection{Communication Hiding}
